---
title: "Course management with ghclass"
author: "Mine Çetinkaya-Rundel"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Course management with ghclass}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Who is this package for?

This package is for everyone! But really, if you're an instructor who uses 
GitHub for your class management, e.g. students submit assignments via GitHub 
repos, this package is definitely for you! The package also assumes that you're 
an R user, and you probably teach R as well, though that's not a requirement 
since this package is all about setting up repositories with the right 
permissions, not what your students put in those repositories. (If you're a 
Python user, see [this post](https://ubc-mds.github.io/2017-08-24-teaching-with-github/) for a Python 
based alternative.)

## What is this vignette about?

This vignette is about the nitty-gritty of setting your class up in GitHub with
ghclass. For a higher level discussion of why and how to use Git/GitHub in data
science education, see [this paper](https://peerj.com/preprints/3181/) by the
package authors.

## Structuring your class on GitHub

The general framework is outlined below. This is not the only way to structure
a class on GitHub, but it's a good way, and one that ghclass is optimized to
work with.

We outline steps for achieving this structure in the next section. This section
is meant to give a high level view of what your course looks like on GitHub.

- One organization per class: If you teach at a university, this means one
semester of a given course. If you teach workshops, this would be one workshop.
The instructor and any additional instructional staff, e.g. teaching
assistants, are owners. Going forward we will refer to this group of people as
"instructors".  The students are members.

- One repo per student (or team) per assignment: The instructors have admin
access to repos, i.e. they can read, clone, push, and add collaborators to
assignment repositories as well as delete them. The students have write access
to repo, which means that they can read, clone, and push to this repository but
they cannot delete them and they cannot add others to them. This can help with
minimizing accidents that cannot be undone and makes sure students cannot peek
into each others' repositories unless you explicitly allow them to do so.

If you have a teamwork component to your course, you can also set up teams on
GitHub and give them access to repositories for team assignments.

Suppose you have 48 students in your class, and they are in 12 teams of 4
students each. Suppose also that students turn in the following throughout a
semester:

- Individual: 10 homework assignments + 2 exams
- Teamwork: 8 lab assignments + 1 project

Then, throughout the semester you will need to create total of

```{r repos}
repo_indiv <- 10 + 2
repo_team <- 8 + 1
48 * repo_indiv + 12 * repo_team
```

That is a lot of repos to create and set permissions to manually! It's also a
lot of repos to clone when it comes time to grading. ghclass addresses this
problem, and more! It does not, however, address the problem that that's a lot
of grading. Sorry, you're on your own there!

That being said, ghclass does also facilitate setting up continuous integration
for students' assignment repos, which means that some of the checking and
feedback giving can be done automatically each time they push to the repo
without intervention from the instructors.

## Authentication

<!-- Still need to decide whether to completely drop the wercker token part -->

This package uses tokens for authentication with both
[wercker](https://app.wercker.com/profile/tokens) and
[github](https://github.com/settings/tokens), these values can be supplied via
environmental variables `GITHUB_TOKEN` and `WERCKER_TOKEN` respectively or in
`~/.github/token` and `~/.wercker/token`.

If this is your first time setting up a personal access token (PAT), generate a
token in the browser after logging into Github (Settings > Developer Settings >
Personal access tokens) or use
[`usethis::browse_github_token`](https://usethis.r-lib.org/articles/articles/usethis-setup.html#get-and-store-a-github-personal-access-token).
Copy your token to the clipboard and paste it as a character string into the
`github_set_token` function.

Alternative token locations can be specified with `github_set_token` or
`set_wercker_token`.

## Step-by-step guide

Start with creating an organization on GitHub for the course. We recommend
using the course number, semester/quarter, and year in the organization name,
e.g. for a course numbered Sta 199 in Spring 18, you can use `Sta199-Sp18`.

Then go [here](https://education.github.com/discount_requests/new) to apply for
GitHub Education discount for unlimited private repositories. This is an
optional step, but one that many will want to do. GitHub charges for private
repositories unless they are used for teaching purposes. The application for
GitHub Education discount requires that you submit a course syllabus and/or a
link to the course homepage. Make sure you have (at least a draft of) a
syllabus ready at this point. Approval is usually pretty quick, but you don't
want to do this the night before classes begin. Give yourself at least a week
to be safe.

### Adding students and creating teams

Next, collect your students' GitHub user names. You can do this with a Google
form and then read the spreadsheet containing their responses into R using the
**googlesheets** package. The resulting data frame should include two columns:
one called `github` which contains students' GitHub user names and another
column called `team` that contains the team name for each student.

For example, your roster file might look something like the following:

```csv
github,team
Alice,Team1
Bob,Team2
Carol,Team3
Dave,Team1
Eve,Team2
```

Using the `roster` data frame, we can then invite the students to the class'
organzation. This will send an email to each student inviting them to join the
GitHub organization.

```r
invite_user("Sta523-Fa17", roster$github)

## Adding Alice to Sta523-Fa17 ...
## Adding Bob to Sta523-Fa17 ...
## Adding Carol to Sta523-Fa17 ...
## Adding Dave to Sta523-Fa17 ...
## Adding Eve to Sta523-Fa17 ...
```

We use the variable `team` within the `roster` data frame to create a vector of unique team names, here called `teams`. We then use the `teams` vector to add students to their teams within the organization via the `team_create()` function.

```r
teams <- unique(roster$team)
team_create("Sta523-Fa17", teams)

## Adding team Team1 to Sta523-Fa17 ...
## Adding team Team2 to Sta523-Fa17 ...
## Adding team Team3 to Sta523-Fa17 ...
```

```r
team_invite("Sta523-Fa17", roster$github, roster$team)

## Adding Alice to team Team1 ...
## Adding Bob to team Team2 ...
## Adding Carol to team Team3 ...
## Adding Dave to team Team1 ...
## Adding Eve to team Team2 ...
```

You can check which students are added to the organization using the
`get_members` function, and pending invitations using the `get_pending_members`
function, respectively. Note that if students are first-time GitHub users, they will need to
verify the email address associated with their GitHub account and accept the
invitation before they show up as a member of the organization.

### Creating a team assignment

First, create repositories for each team in the `teams` vector; with a prefix identifying the
assignment. The resulting repo names will be this prefix followed by the team
name.

```r
create_team_repo("Sta523-Fa17", teams, prefix="hw2-")

## Creating repo Sta523-Fa17/hw2-Team1 ...
## Creating repo Sta523-Fa17/hw2-Team2 ...
## Creating repo Sta523-Fa17/hw2-Team3 ...
```

If you want to place starter docs into the assignment repos that you just
created, you should first create a repo in this organization containing these
starter docs and then mirrow the contents of that repo to the repos you created
earlier. You can do this with the `mirror_repo` function.

```r
mirror_repo(
  source_repo = "Sta523-Fa17/hw2",
  target_repos = get_repos("Sta523-Fa17","hw2-")
)

## Cloning source repo (Sta523-Fa17/hw2) ...
## Mirroring Sta523-Fa17/hw2 to Sta523-Fa17/hw2-Team1 ...
## Mirroring Sta523-Fa17/hw2 to Sta523-Fa17/hw2-Team2 ...
## Mirroring Sta523-Fa17/hw2 to Sta523-Fa17/hw2-Team3 ...
## Cleaning up ...
```

### Creating an individual assignment

The process for creating an individual assignment is very similar to that for
creating a team assignment, but uses the `create_individual_assignment()`
function instead.

### Adding Wercker badges to repos

Before running the following step(s) involving Wercker make sure you've done
the following:

* If you do not have one already create an account with Wercker

* Create an organization with Wercker that will contain all of your apps for this class

* Create and save a Wercker [token](https://app.wercker.com/profile/tokens) to `~/.wercker/token`

* Make sure third party access is allowed for your github organization (See Settings / Third-party access then click on remote restrictions)

```r
add_wercker(get_repos("Sta523-Fa17", "hw2-"), "Sta523-Fa17")

## Creating wercker app for Sta523-Fa17/hw2-Team1 ...
## Creating wercker app for Sta523-Fa17/hw2-Team2 ...
## Creating wercker app for Sta523-Fa17/hw2-Team3 ...
```

### Modifying repos

<!-- This part needs to be changed based on the discussion regarding GH issue
#16 -->

You can modify repos after they have been created. This will overwrite existing
files with the same name in the repo, so you should be careful not to do this
if students have already started working on the repos.

```r
add_files(
  get_repos("Sta523-Fa17","hw2-"),
  message = "Remove wrong wercker badge",
  files = "~/Desktop/Sta523/Homework/hw2/repo/README.md"
)

## Adding files to Sta523-Fa17/hw2-Team1 ...
## Adding files to Sta523-Fa17/hw2-Team2 ...
## Adding files to Sta523-Fa17/hw2-Team3 ...
```

### Managing repository permissions
Individual-level permissions can be set via the "People" tab on the
organization page. We recommend the course instructor to be the owner of the
organization and teaching assistants to receive admin privileges. Students
should receive member privileges.

Github allows further permissions for accessing and changing repositories to be
set for each individual member or at the organization-level (under Settings >
Member Privileges). We suggest the organization-level settings below.

*Member repository permissions*

* Base permissions: None
* Repository creation: Disabled
* Repository forking: Disabled

*Admin repository permissions*

* Repository visibility change: Disabled
* Repository deletion and transfer: Disabled
* Issue deletion: Disabled

*Member team permissions*

* Allow members to create teams: Disabled


## FAQ

1. Do I really need private repositories for my students' assignments? I don't
care if they see each others' work.

You might not care, but the law might. For example, in the United States, FERPA
regulations stipulate that student information should be kept private. If you
use public repositories, anyone can find out who is enrolled in your course.
Additionally, you will likely be using GitHub issues for providing feedback on
the students' work, and potentially even mention their grade in a given
assignment. This information should not be publicly available to anyone.

Also, your students may not want their coursework to be publicly available.
They are bound to make mistakes as they learn and it should be up to them
whether they want those to be a piece of their public profile on GitHub.

2. Why not use [GitHub Classroom](https://classroom.github.com/)?

At some level this is a matter of preference, but there are a few
functionalities here that are not present in GitHub Classroom:

- Pre-defined teams -- as opposed to relying on students to pick their team when
creating their assignment repo.
- Command-line interface -- if you like writing R code to solve your problems
this may be a better fit for you as it provides a greater level of control and
more flexibility.
- Actually you don't have to choose between ghclass and [GitHub Classroom](https://classroom.github.com/), your workflow might involve using both.
